Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Changed the World

### 2015-12-16 paper.tex
add refference for medicinal use of cordyceps

\begin{figure}[!ht]
    \centering
    \includegraphics[width=.4\textwidth]{images/WolbachiaTree.jpg}
    \caption{ A depiction of the strain distribution for Wolbachia. Most importantly, the separation between group A and group B is depicted. \cite{Wtree_image} }
    \label{fig:wolbachiha_tree}
\end{figure}

@@

@@

- Cordyceps has been studied to make an immuno-surpressant drug
- Cordyceps is necessary for keeping bug populations in check
- Toxoplasma has been correlated to a rise in schizophernia
- Wolbachia has made us question evolution
- Infecting insects with Wolbachia causes them to not carry dengue fever
- Targetting Wolbachia to treat filarial infections is effective.

>>>>

\begin{figure}[!ht]
    \centering
    \includegraphics[width=.4\textwidth]{images/WolbachiaTree.jpg}
    \caption{ A depiction of the strain distribution for Wolbachia. Most importantly, the separation between group A and group B is depicted. \cite{Wtree_image} }
    \label{fig:wolbachia_tree}
\end{figure}

@@

In fact, there is a lot of research that needs to be done on \textit{Wolbachia} in general. There is still so much that is not known about the bacteria, even how many organisms it infects is a mystery. However, there is another microbe which might be even more mysterious than the \textit{Wolbachia}.

@@

- Cordyceps has been studied to make an immuno-surpressant drug
A cousin of the and manipulating fungus \textit{Cordyceps sinensis} \cite{medicinal_cordy}
- Cordyceps is necessary for keeping bug populations in check
- Toxoplasma has been correlated to a rise in schizophernia
- Wolbachia has made us question evolution
- Infecting insects with Wolbachia causes them to not carry dengue fever
- Targetting Wolbachia to treat filarial infections is effective.
